PM Component Paper Plots

### 2021-02-14 code/data-processors/cms-data-processor.Rmd
modified factor data names - shape and color plots - mass apportionemnt

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
load(paste0(dirUSSpatial,'brfss-site.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','master-ndi-pmc-race.RDa'))
load(here('data','processed','master-ndi-pmc-bz6.RDa'))
load(here('data','processed','master-ndi-pmc-bz12.RDa'))
load(here('data','processed','master-ndi-pmc-bz24.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ex-ec-1yr.RDa'))
load(here('data','processed','pmc-residual-1yr.RDa'))
load(here('data','processed','fac-ex-ec-residual-1yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
```

@@

```{r Factors}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

@@

dt.ndi.fac.ex.ec <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.ex.ec, 
          file = here('data', 'processed', 'ndi-fac-ex-ec.csv'),
          row.names = F)
```

@@

```{r Factors Excluding EC Residual}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.fac.ex.ec.residual <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_enrollee:no_death_lungc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.ex.ec.residual.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.ex.ec.residual, 
          file = here('data', 'processed', 'ndi-fac-ex-ec-residual.csv'),
          row.names = F)
```

@@

### LE 75
dt.ndi.fac.ageLE75 <- dt.age %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aLE75 = ifelse(age == "LE", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### M 75
dt.ndi.fac.ageM75 <- dt.age %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aM75 = ifelse(age == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.sex <- dt.master.ndi.pmc %>% 
    select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses)

@@

dt.ndi.fac.raceA <- dt.raceA %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rA = ifelse(race == "A", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.fac.raceB <- dt.raceB %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rB = ifelse(race == "B", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.fac.raceH <- dt.raceH %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rH = ifelse(race == "H", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.fac.raceW <- dt.raceW %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rW = ifelse(race == "W", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Urban and Suburban
dt.ndi.fac.urban <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(urb = ifelse(!Location.Setting == "RURAL", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Location.Setting)

@@

### Rural
dt.ndi.fac.rural <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rur = ifelse(Location.Setting == "RURAL", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Location.Setting)

@@

### West = 1
dt.ndi.fac.west <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rW = ifelse(Region.IV == 1, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

@@

### Midwest = 2
dt.ndi.fac.midwest <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rMW = ifelse(Region.IV == 2, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

@@

### South = 3
dt.ndi.fac.south <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rS = ifelse(Region.IV == 3, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

@@

### Northeast = 4
dt.ndi.fac.northeast <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rNE = ifelse(Region.IV == 4, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

>>>>

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
load(paste0(dirUSSpatial,'brfss-site.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','master-ndi-pmc-race.RDa'))
load(here('data','processed','master-ndi-pmc-bz6.RDa'))
load(here('data','processed','master-ndi-pmc-bz12.RDa'))
load(here('data','processed','master-ndi-pmc-bz24.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-residual-1yr.RDa'))
load(here('data','processed','fac-residual-1yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
```

@@

```{r Factors with EC}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.fac.ec <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.fac.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.ec, 
          file = here('data', 'processed', 'ndi-fac-ec.csv'),
          row.names = F)
```

@@

@@

```{r Factors Residual}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.fac.residual <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_enrollee:no_death_lungc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.residual.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.residual, 
          file = here('data', 'processed', 'ndi-fac-residual.csv'),
          row.names = F)
```

@@

### LE 75
dt.ndi.fac.ageLE75 <- dt.age %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aLE75 = ifelse(age == "LE", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### M 75
dt.ndi.fac.ageM75 <- dt.age %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aM75 = ifelse(age == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.sex <- dt.master.ndi.pmc %>% 
    select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses)

@@

dt.ndi.fac.raceA <- dt.raceA %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rA = ifelse(race == "A", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.fac.raceB <- dt.raceB %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rB = ifelse(race == "B", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.fac.raceH <- dt.raceH %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rH = ifelse(race == "H", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.fac.raceW <- dt.raceW %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rW = ifelse(race == "W", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Urban and Suburban
dt.ndi.fac.urban <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(urb = ifelse(!Location.Setting == "RURAL", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Location.Setting)

@@

### Rural
dt.ndi.fac.rural <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rur = ifelse(Location.Setting == "RURAL", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Location.Setting)

@@

### West = 1
dt.ndi.fac.west <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rW = ifelse(Region.IV == 1, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

@@

### Midwest = 2
dt.ndi.fac.midwest <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rMW = ifelse(Region.IV == 2, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

@@

### South = 3
dt.ndi.fac.south <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rS = ifelse(Region.IV == 3, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

@@

### Northeast = 4
dt.ndi.fac.northeast <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rNE = ifelse(Region.IV == 4, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

### 2021-02-14 code/data-viz/forest-plots-color.Rmd
modified factor data names - shape and color plots - mass apportionemnt

###color codes: https://www.schemecolor.com/british-airways-website.php

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-age.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
ggsave(here('output', 'plot','fac-age.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-sex.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
ggsave(here('output', 'plot','fac-sex.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-race.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
ggsave(here('output', 'plot','fac-race.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-urbanicity.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
ggsave(here('output', 'plot','fac-urbanicity.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-sescat.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
ggsave(here('output', 'plot','fac-region.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-resid-region.png'),width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-brfss.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-buffer.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) + 
ggsave(here('output', 'plot','pmc-expo.png'), width = 6.5, height = 8.5)
```

>>>>

### plots subgroups using different colors
###color codes: https://www.schemecolor.com/british-airways-website.php

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-age.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-age.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sex.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-sex.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-race.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-race.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-urbanicity.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-urbanicity.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sescat.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-region.png'), width = 6.5, height = 6.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-resid-region.png'),width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-brfss.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-buffer.png'), width = 6.5, height = 7.5)
```

@@

Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
ggsave(here('output', 'plot','pmc-expo.png'), width = 6.5, height = 8.5)
```
